---
title: "Bezier Curves"
author: "Hussain Alsalman"
date: "5/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Objective 
This notebook is an attempt to understand bezier curves and use them to draw custom drawings using the `grid` package. 

# The mathimatics behind Bezier Curves

Bezier curves are some form of "parametric functions" which is basically a function that yeild multiple outputs by using multiple functions. 

let's take an example 

$f(x) = cos(x)$ this is an example of a simple function 

let's make more so we get to the parametric stuff 

$$
f(a) = cos(a) \\
f(b) = sin(b)
$$


$$
\begin{cases}
f_{a}(t) = cos(t) \\
f_{b}(t) = sin(t)
\end{cases}
$$

```{r}
library("grid")

x <- c(120,35,220,220)
y <- c(160,200,260,40)
grid.newpage()
grid.bezier(x,y, )

```

```{r}
library(grid)

grid.newpage()

grid.rect(x = 0.1, y = 0.4, width = unit(0.18, "npc"), 
          height = unit(0.6, "npc"))
grid.rect(x = 0.65, y = 0.4, width = unit(0.6, "npc"), 
          height = unit(0.6, "npc"))

for (i in c(0.1, 0.17)) {
  x <- c(0.08, 0.05, i, 0.08)
  y <- c(0.15, 0.25, 0.25, 0.5)
  grid.bezier(x, y, gp = gpar(col = "green3"))
}

for (i in c(0.38, 0.8)) {
  x <- c(0.4, i, i, 0.9)
  y <- c(0.4, i, 0.15, 0.15)
  grid.bezier(x, y, gp = gpar(col = "blue3"))
}
```

